---
title: "Internship Report Title"
subtitle: "Internship Report Subtitle"
author: "Name Surname"
scope: "Internship Report"
academicyear: "202x-202x"
supervisor:
    - prefix: "Supervisor"
    - name: "Name Surname"
cosupervisor:
    - prefix: "Co-Supervisor"
    - name: "Name Surname"
format:
  internship-report-pdf: default
logo: "img/unipd.pdf"
csl: "https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl"
bibliography: "files/references.bib"
crossref:
  lof-title: "List of Figures"
  lot-title: "List of Tables"
  fig-prefix: "Figure"
  fig-title: "Figure"
  tbl-prefix: "Table"
  tbl-title: "Table"
---

# Writing in Markdown

Markdown is a very easy and intuitive markup language that can be converted to any other document format using [Pandoc](https://pandoc.org/).

Learning Markdown is very easy and there are multiple online resources:

- [https://www.markdowntutorial.com/](https://www.markdowntutorial.com/)
- [https://www.markdownguide.org/getting-started/](https://www.markdownguide.org/getting-started/)

## What about Quarto?

Quarto is an open-source scientific and technical publishing system that combine (Pandoc) Markdown with programming languages (e.g., R) to create high-quality documents in different formats e.g. pdf or html. Quarto has a very detailed and extensive documentation [https://quarto.org/docs/guide/](https://quarto.org/docs/guide/).

## Include references

References are easily implemented in Quarto. You need to specify a **bibtex** file in the YAML frontmatter `bibliography: file.bib` and then start citing the references using the bibtex keys. See the Quarto documentation [https://quarto.org/docs/authoring/footnotes-and-citations.html](https://quarto.org/docs/authoring/footnotes-and-citations.html).

For example using `@Lakens2018-ri` produce @Lakens2018-ri. To create a citation within parentheses you can use `[@Lakens2018-ri]` producing [@Lakens2018-ri]. You can also cite multiple sources as [@Lakens2018-ri; @Liddell2018-wu]

## Including images

External images (i.e., where you have a file) can be included using the markdown/Quarto syntax (see the Quarto documentation [https://quarto.org/docs/authoring/figures.html](https://quarto.org/docs/authoring/figures.html)). For example using `![This is my nice figure caption](img/unipd.pdf)` will include the image:

![This is my nice figure caption](img/unipd.pdf){#fig-unipd-logo}

If you define a label for the image (see [https://quarto.org/docs/authoring/figures.html#cross-references](https://quarto.org/docs/authoring/figures.html#cross-references)) you can also refer to it in the text without worrying about the actual number. For example you can say "as seen in `@fig-unipd-logo`" and `@fig-unipd-logo` will be replaced by the prefix "Figure" and the number of the figure. For example, @fig-unipd-logo shows the logo of the University of Padova.

Images can be also produced by R for example from the `plot()` function. The following code chunk will create an histogram presented in @fig-hist.

```{r}
#| eval: false
hist(rnorm(100), breaks = 50, col = "dodgerblue")
```

```{r}
#| echo: false
#| label: fig-hist
#| fig-cap: This is a nice histogram
hist(rnorm(100), breaks = 50, col = "dodgerblue")
```

\newpage

# References {-}

::: {#refs}
:::